
```{r}
install.packages('lubridate') 
install.packages('Hmisc') 
install.packages('tidyverse') 
install.packages('ggplot2') 
install.packages('dplyr') 
install.packages('tidyquant')
install.packages('quantmod')
install.packages('TSstudio')
install.packages('tseries')
install.packages('MASS')
install.packages('forecast')
install.packages('TSA')


library('lubridate')
library('Hmisc')
library('tidyverse')
library('ggplot2')
library('dplyr')
library('tidyquant')
library('quantmod')
library('TSstudio')
library('tseries')
library('MASS')
library('forecast')
library('TSA')
```

##Data Processing
```{r}
data <- read.csv(file = '~/Desktop/STAT485/Microsoft_Stock.csv')
print(data)
```
```{r}
summary(data)
```

```{r}
describe(data)
```


#since we are working with time series, the most essential features are the time related feature. And in the summary, we can see that the data feature is still character, so we need to convert datatime to index in this example.

```{r}
data$Date <- as.Date(mdy_hms(data$Date))
print(data)
```

```{r}
rownames(data) <- data[,1]
print(data)
```

##Data Visualization

```{r}
ts_plot(data,
        title = "Over view",
        slider = TRUE,
        type = "multiple")
```

```{r}
data_use <- data[,-1]
```


```{r}
stock_close <- ts(data_use$Close, start=c(2015,4),end=c(2019,3),frequency = 12)
stock_open <- ts(data_use$Open, start=c(2015,4),end=c(2019,3),frequency = 12)
print(stock_close)
print(stock_open)
```
```{r}
plot(stock_close,type='o',main='Two series',xlab='Time',ylab='Time series',col='blue')
lines(stock_open,type='o',col='red')
legend('topleft',legend=c('close','open'), lty=c(1,1),col=c('blue','red'))
```


```{r}
lnstock = log(stock_close[1:48])
lnstock
```

```{r}
acf(lnstock, lag.max = 20)
```
we have a very gradual descent in our lags so each line going up represents the degree of correlation between our lags.

```{r}
pacf(lnstock, lag.max = 20)
```
we have an immediate drop in the first lag, meaning that all the higher-order autocorrelations are effectively explained by the first lag autocorrelation.


##Stationarity
#In order to apply a time series model, we need to identify if the dataset is stationary.
#Phillips-Perron Test
```{r}
pp.test(lnstock,alternative="stationary")
```
```{r}
difflnstock=diff(lnstock,1)
difflnstock
```
```{r}
pp.test(difflnstock,alternative="stationary")
```
#We have a p-value of 0.908 for our original in time series, indicates non stationarity. However for the time series that we differenced, we now have a p-value of 0.01 so that indicates at the 5% level we can reject a null hypothesis of non stationarity.

##need redo the stationary test.

#ADF test
```{r}
adf.test(data$Open)
adf.test(data$Close)
```
Same conclusion.

##
use close and open(stock_close and stock_open)
(close as the first choice)

#Non-seasonal ARIMA
fit <- Arima(lnstock, order=c(0,1,0), include.constant=TRUE, method='ML') 
Arima(data, order=c(1,1,0), include.constant=TRUE, method='ML') 
Arima(data, order=c(1,1,1), include.constant=TRUE, method='ML') 
#AR(1) --> tutorial 4/5 could test with different phi

#AR(2)?? --> tutorial 6

#compare AR(2) and ARMA(2,1)?? --> tut 7/8

#More model to choose

#compare(?)





